A Large-scale Study of Polymorphism in R

### 2019-03-29 paper/main.tex
fighting git
updated loc counts
merging
more corpus prose

\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{booktabs,listings,xspace,wrapfig}
\lstset{language=R}
\usepackage{my_style}

\definecolor{LightGray}{rgb}{.95,.95,.95}
\definecolor{Gray}{rgb}{.3,.3,.3}
\definecolor{DarkGray}{rgb}{.5,.5,.5}

@@

Figure~\ref{most} shows the ten most downloaded CRAN packages.  For each
one, we list how many lines of R and C/C++ the packages contains.
Typically, C/C++ code is used to implement performance critical portions of
the code. We show the number of scripts that could be extracted from the
package. Each script corresponds to either one use-case or a set of unit
tests.  Figure~\ref{allcloc} shows the size of the code across all the
packages we have used.  Lastly, Figure~\ref{recorded} gives the number of
function signatures that we recorded while executing the scripts of each
package.

\AT{TODO Touch up graphs.}

@@

% https://www.r-pkg.org/downloaded
\begin{figure}[!th]{\footnotesize\begin{tabular}{@{}r||l|r|r|r|r|r@{}}\hline
\bf Package & \bf Description & \bf R LOC &\bf C LOC &\bf Scripts & \bf Calls Observed & \bf Calls Recorded \\
\hline
\tt Rcpp  & Seamless C++ integration & 2.1K & 4K & 25 & 55K & 282 \\
\tt rlang & Functions for 'Tidyverse' & 4.4K & 3.8K & 122 & 3,924K & 5,171 \\
\tt glue  & Interpreted string literals & 0.2K & 0.2K & 8 & 4K & 120 \\
\tt tibble & Simple data frames & 1.3K & 0.3K & 16 & 1,332K & 4,148 \\
\tt stringi &  String processing & 1.5K & 515K & 64 & 923K & 666 \\
\tt ggplot2 & Data visualisations & 10.8K & 0 & 130 & 153K & 2,636\\
\tt dplyr  &  Data manipulation & 3.8K & 4.7K & 78 & 233K & 1,967 \\
\tt pillar & Formatting for columns & 1.3K & 0 & 13 & 803K & 1,273 \\
\tt R6 & Classes w. ref. semantics & 0.6K & 0 & 2 & 1K & 226 \\
\tt stringr & String operations & 0.5K & 0 & 32 & 1,764K & 371 \\
\end{tabular}}\caption{10 Most Downloaded Packages.}\label{most}
\end{figure}

>>>>

\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{booktabs,listings,xspace,wrapfig}
\lstset{language=R}
\usepackage{my_style}
\definecolor{LightGray}{rgb}{.95,.95,.95}
\definecolor{Gray}{rgb}{.3,.3,.3}
\definecolor{DarkGray}{rgb}{.5,.5,.5}

@@

Figure~\ref{most} shows the ten most downloaded CRAN packages.  For each
one, we list how many lines of R and C/C++ the packages contains.
Typically, C/C++ code is used to implement performance critical portions of
the code. We show the number of scripts that could be extracted from the
package. Each script corresponds to either one use-case or a set of unit
tests.

Figure~\ref{allcloc} shows the size of the code across all the packages we have used. 
The lines of R code are above the X-axis, and lines of C code below.
All counts are $log_{10}$-scaled, and entries are in ascending order by number of lines of R.
Roughly speaking, the majority of R packages have between 100 and 1000 lines of code.
In terms of C, only ~25\% of packages have any C code.
C and C++ are often used to implement parts of a package where performance is critical.

Lastly, Figure~\ref{recorded} plots the relationship between recorded and observed signatures.
Here, \# observed $>$ \# recorded since it's impossible to record more traces than those which pass through the tracer.
Numbers are again $log_{10}$-scaled.

\AT{TODO Touch up graphs.}
\AT{TODO Other interesting plots? Recorded vs \# scripts?}

Having built a sense for the corpus of data that we're dealing with, we will turn our attention to our methods of data collection.

@@

% https://www.r-pkg.org/downloaded
\begin{figure}[!th]{\footnotesize\begin{tabular}{@{}r||l|r|r|r|r|r@{}}\hline
\bf Package & \bf Description & \bf R LOC &\bf C LOC &\bf Scripts & \bf Calls Observed & \bf Calls Recorded \\
\hline
\tt Rcpp  & Seamless C++ integration & 2.2K & 4.2K & 25 & 55K & 340 \\
\tt rlang & Functions for 'Tidyverse' & 7.0K & 6.1K & 122 & 3,924K & 8,422 \\
\tt glue  & Interpreted string literals & 0.3K & 0.3K & 8 & 4K & 145 \\
\tt tibble & Simple data frames & 2.0K & 0.3K & 16 & 1,332K & 6,367 \\
\tt stringi &  String processing & 1.5K & 515K & 64 & 923K & 873 \\
\tt ggplot2 & Data visualisations & 14K & 0 & 130 & 153K & 4,608 \\
\tt dplyr  &  Data manipulation & 4.5K & 4.7K & 78 & 233K & 3,099 \\
\tt pillar & Formatting for columns & 1.4K & 0 & 13 & 803K & 1,514 \\
\tt R6 & Classes w. ref. semantics & 0.7K & 0 & 2 & 1K & 330 \\
\tt stringr & String operations & 0.5K & 0 & 32 & 1,764K & 534 \\
\end{tabular}}\caption{10 Most Downloaded Packages.}\label{most}
\end{figure}
